%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This document is based on a template available at
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
% taken from: https://github.com/AmeliaMN/CV/blob/master/CV.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[]{resume}

\usepackage[margin=1in]{geometry}

\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=violet,
    filecolor=black,      
    urlcolor=violet,
    citecolor = black
}
\usepackage{halloweenmath}

\usepackage{enumitem}
\setitemize{itemsep=0pt}

% Need to include this for refs with Pandoc
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}
{\setlength{\parindent}{0pt}
\everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}
{\par}

\usepackage{titlesec}
\titleformat{\section}[block]{\bfseries}{}{1em}{}
\setcounter{secnumdepth}{0}

\name{Lucy E Delaney} 
\address{\href{mailto:ldelan5@uic.edu}{\nolinkurl{ldelan5@uic.edu}} \\ \url{ledelaney.org}  \\ @\href{https://twitter.com/emergentlyLucy}{emergentlyLucy} } 
\address{Department of Biological Sciences \\ University of Illinois at Chicago \\ Chicago,
IL 60622} 


\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[R]{\tiny{January 8,
2021 | page \thepage\ of \pageref{LastPage}}\\\tiny{L E Delaney printable CV; \href{https://github.com/ledelaney/rmd-cv}{all resources available here.}}}

\begin{document}


\begin{rSection}{Interests}
Conceptual understanding of evolutionary principles, evolution-centered
teaching, \texttt{R} for \linebreak undergraduate education,
macroevolution, the evolution of plant breeding systems, data
\linebreak manipulation \& visualization with \texttt{tidyverse}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

	\textbf{Ph.D candidate, Ecology \& Evolutionary Biology} \hfill 2022\\ 
	University of Illinois at Chicago \hfill Chicago, IL\\
     
    \vspace{-0.7cm}
     Dissertation: \emph{The Nature of Adaptation and the Epistemology
of Natural Selection} \vspace{0.3cm}

      

	\textbf{M.A., Molecular \& Cellular Biology} \hfill 2016\\ 
	Hunter College (CUNY) \hfill New York, NY\\
     

	\textbf{B.S., Forensic Molecular Biology, Philosophy} \hfill 2012\\ 
	John Jay College (CUNY) \hfill New York, NY\\
     


\end{rSection}

%----------------------------------------------------------------------------------------
%	UNIVERSITY TEACHING
%----------------------------------------------------------------------------------------

\begin{rSection}{University Teaching}
    \textbf{BIOS 220} Mendelian and Molecular Genetics \hfill Fall 2019
- Summer 2020
     
    \vspace{-0.30cm}
     Sophomore-level course focusing on Mendelian inheritance patterns
and molecular mechanisms of inheritance. Helped managed transition from
in-person to online delivery. Responsible for teaching discussion
section, creating digital course materials \& exams, grading, and
Blackboard administration.\\
     
\vspace{-0.3cm}

    \textbf{BIOS 331} General Ecology Laboratory \hfill Summer 2019
     
    \vspace{-0.30cm}
     Application of ecological and evolutionary concepts with hands-on
experiments and field trips to local natural areas. Responsible for
weekly laboratory instruction, office hours, and grading.\\
     
\vspace{-0.3cm}

    \textbf{BIOS 230} Ecology and Evolution \hfill Spring 2019
     
    \vspace{-0.30cm}
     Sophomore-level course with emphasis on basic ecological systems,
ecosystem dynamics, and evolutionary principles. Responsible for weekly
office hours, assignment creation, and grading.\\
     
\vspace{-0.3cm}

    \textbf{BIOS 430} Evolution \hfill Fall 2017 - Fall 2018
     
    \vspace{-0.30cm}
     Upper-division, programming-focused course on evolutionary theory
and principles. Responsible for weekly office hours \& debugging, quiz
materials, and grading of \texttt{R} programming
\linebreak assignments.\\
     
\vspace{-0.3cm}

    \textbf{BIOS 120} Biology of Populations and
Communities \hfill 2016-2017
     
    \vspace{-0.30cm}
     Introductory biology laboratory course with emphasis on ecological
and evolutionary principles. Responsible for weekly laboratory
instruction, office hours, and grading.\\
     
\vspace{-0.3cm}

\end{rSection}

%----------------------------------------------------------------------------------------
%	COMMUNITY TEACHING
%----------------------------------------------------------------------------------------

\begin{rSection}{Community Teaching}
    \textbf{Course Builder \& Trainer} UIC Biological Sciences
Department \hfill 2020-Present
     
    \vspace{-0.30cm}
     Trained in online instructional design \& pedagogy, and software
relevant to online teaching \& learning. Assisting Biological Sciences
Department faculty members in transitioning their courses online, and
managing technical aspects of courses throughout online delivery.\\
     
\vspace{-0.3cm}

    \textbf{Tutor} Nurturing Wisdom Tutoring \hfill 2018-2020
     
    \vspace{-0.30cm}
     Highly-rated individual tutoring for grades 7-12 in test
preparation (SAT and high school entrance exams), science, mathematics,
and writing.\\
     
\vspace{-0.3cm}

    \textbf{Substitute Teacher} Chicago-area Charter
Schools \hfill 2015-2016
     
    \vspace{-0.30cm}
     Substitute teacher for elementary, middle, and high school
classes.\\
     
\vspace{-0.3cm}

\end{rSection}


%----------------------------------------------------------------------------------------
% TEACHING HONORS AND AWARDS
%----------------------------------------------------------------------------------------

\begin{rSection}{Teaching Honors and Awards}
\textbf{2020}\ Nominated for the UIC Graduate Student Excellence in
Teaching and Mentoring Award

\textbf{2020}\ Recipient of the Biological Sciences Department Graduate
Teaching Award for BIOS 220

\textbf{2018}\ Recipient of the Biological Sciences Department Graduate
Teaching Award for BIOS 430

\end{rSection}

%----------------------------------------------------------------------------------------
% OTHER AWARDS AND TRAINING
%----------------------------------------------------------------------------------------


\begin{rSection}{Other Awards and Training}
\textbf{2020}\ Participant in the
\href{https://chircollab.github.io/}{2020 Chicago R Collaborative Conference}

\textbf{2018}\ Recipient of the Biological Sciences Department Travel
Award

\textbf{2018}\ Reviewer for International Journal of Botany, Oxford
Bibliographies

\textbf{2017}\ Accepted to NSF-funded workshop on
\href{http://bamm-project.org/index.html}{Bayesian analysis of macroevolutionary mixtures}

\textbf{2017}\ Recipient of the Biological Sciences Department Travel
Award

\textbf{2017}\ Accepted to
\href{https://web.archive.org/web/20170922060558/http://arboretum.harvard.edu/tracing-evolution-form-function/}{microMORPH Plant Anatomy Summer Course}
at Harvard University

\textbf{2016}\ General horticulture volunteer at Garfield Park
Conservatory

\end{rSection}


%----------------------------------------------------------------------------------------
%	PRESENTATIONS and PUBLICATIONS
%----------------------------------------------------------------------------------------
\hypertarget{presentations}{%
\section{PRESENTATIONS}\label{presentations}}

\hrule

\textbf{2021} Society for the Advancement of Biology Education Research
West \hspace{1mm}\textbar{}\hspace{1mm} Talk \vspace{-0.25cm}

\begin{quote}Delaney, Lucy E, \href{https://ledelaney.org/talks/sabertalk/SABER-slides.html}{The Four Causes of Adaptation.}\end{quote}

\textbf{2021} Undergraduate Biology Education Research GRS
\hspace{1mm}\textbar{}\hspace{1mm} Poster \vspace{-0.25cm}

\begin{quote}Delaney, Lucy E, \href{NA}{The Four Causes of Adaptation. \textit{Forthcoming}.}\end{quote}

\textbf{2018} Annual Meeting of the Botanical Society of America
\hspace{1mm}\textbar{}\hspace{1mm} Poster \vspace{-0.25cm}

\begin{quote}Delaney, Lucy E, Ramanauskas, K., \& Igi\'c, B., \href{https://ledelaney.org/static/posters/poster.png}{Breeding Systems in the Legumes.}\end{quote}

\textbf{2017} microMORPH Summer Course
\hspace{1mm}\textbar{}\hspace{1mm} Talk \vspace{-0.25cm}

\begin{quote}Delaney, Lucy E, \href{https://www.dropbox.com/s/o7hcg5riw97wf9i/08-2017-microMORPH.pdf?dl=1}{Evolutionary Consequences of Plant Mating Systems.}\end{quote}

\hypertarget{publications}{%
\section{PUBLICATIONS}\label{publications}}

\hrule
\setlength{\leftmargin}{1.8em}

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-delaney2021}{}%
\textbf{Delaney, Lucy E}, Ramanauskas, K., \& Igić, B. (2021a). Breeding
systems in the legumes: What do we know? \emph{Manuscript in Prep.}

\leavevmode\hypertarget{ref-delaney2021a}{}%
\textbf{Delaney, Lucy E}, Ramanauskas, K., \& Igić, B. (2021b). Breeding
systems in the orchids. \emph{Manuscript in Prep.}

\leavevmode\hypertarget{ref-delaney2012}{}%
\textbf{Delaney, Lucy E}. (2012). Nietzsche, nerve stimulation-image
connection, and ontology. \emph{John Jay's Finest}, \emph{27}, 99--103.
\end{cslreferences}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Programming: R \\
 & Document markup: \LaTeX, HTML \& CSS, R Markdown \\

Licenses & Illinois Substitute Teaching, FCC Technician Class Radio \\
Software & Adobe Illustrator, Microsoft Office Suite  \\


\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%	Professional Experience
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Experience}
    \textbf{Forensic Molecular Biologist} at NYC Office of Chief Medical
Examiner \hfill 2012-2015
     
    \vspace{-0.30cm}
     Examined evidence for the presence of biological fluids, performed
     serological \& DNA analysis techniques, analyzed data \& performed
     statistical analyses, wrote reports, and provided expert scientific
     testimony in court.
     
    \vspace{0.4cm}
    \textbf{Health Research Intern} at NYC Department of
Health \hfill 2011-2012
     
    \vspace{-0.30cm}
     Accepted to the Health Research Training Program for a year-long
     internship with the Bureau of Environmental Disease Prevention.
     Received training in disease epidemiology, emergency preparedness
     \& response, public health and outreach programs in environmental
     disease control \& prevention, and emerging viral infections.
     
    \vspace{0.4cm}
\end{rSection}

\end{document}