---
output:
  pdf_document:
    latex_engine: xelatex
    template: template.tex
date: July 3, 2020
first: "Lucy E"
last: "Delaney"
email: "ldelan5@uic.edu"
address: "Chicago, IL 60622"
website: "ledelaney.github.io/"
googlescholar: 
orcid: 
programming: "R, CSS"
languages: "$\LLaTeX$, HTML, Markdown, & RMarkdown"
github: "ledelaney"
twitter: 
licenses: "Illinois Substitute Teaching License & FCC Technician Class Radio License"
interests: "Evolution outreach & education, macroevolution, the evolution of plant breeding systems, the nature of adaptation, data manipulation & visualization with `tidyverse`, `R` for undergraduate education"
edu:
  - {degree: PhD student, where: University of Illinois at Chicago, description_1: "in Ecology & Evolutionary Biology", description_2: "Thesis: _The Process of Natural Selection: Resultant patterns and how we understand them_"}
  - {degree: MA, where: "Hunter College (CUNY)", description_1: "in Molecular & Cellular Biology, 2016"}
  - {degree: BS, where: "John Jay College (CUNY)", description_1: "in Forensic Molecular Biology, Philosophy, 2012"}
  
class:
  - {year: "2019-Present", what: "BIOS 220", description_1: "Mendelian and Molecular Genetics", description_2: "Sophomore-level course focusing on Mendelian inheritance patterns and molecular mechanisms of inheritance. Helped managed transition from in-person to online delivery. Responsible for teaching discussion section, creating digital course materials & exams, grading, and Blackboard administration."}
  - {year: "Spring 2019", what: "BIOS 230", description_1: "Ecology and Evolution", description_2: "Sophomore-level course with emphasis on basic ecological systems, ecosystem dynamics, and evolutionary principles. Responsible for weekly office hours, assignment creation, and grading."}
  - {year: 2017-2018, what: "BIOS 430", description_1: "Evolution", description_2: "Upper-division, programming-focused course on evolutionary theory and principles. Responsible for weekly office hours & debugging, quiz materials, and grading of `R` programming assignments."}
  - {year: 2016-2017, what: "BIOS 120", description_1: "Biology of Populations and Communities", description_2: "Introductory biology laboratory course with emphasis on ecological and evolutionary principles. Responsible for weekly laboratory instruction, office hours, and grading."}

work:
  - {year: "2020-Present", where: "at UIC Biological Sciences Department", what: "Online Course Builder", description: "Trained in online instructional design & pedagogy, and software relevant to online teaching & learning. Assisting Biological Sciences Department faculty members in transitioning their courses online, and managing technical aspects of courses throughout online delivery."}
  - {year: "2018-Present", where: "at Nurturing Wisdom Tutoring", what: "Tutor", description: "Highly-rated individual tutoring for grades 7-12 in test preparation (SAT and HSETs), science, mathematics, and writing."}
  - {year: 2012-2015, where: "at NYC Office of Chief Medical Examiner", what: "Forensic Molecular Biologist", description: "Examined evidence for the presence of biological fluids, performed serological & DNA analysis techniques, analyzed data & performed statistical analysis, wrote reports, and provided expert scientific testimony in court."}
  - {year: 2011-2012, where: "at NYC Department of Health", what: "Health Research Intern", description: "Accepted to the Health Research Training Program for a year-long internship with the Bureau of Environmental Disease Prevention. Received training in disease epidemiology, emergency preparedness & response, public health and outreach programs in environmental disease control & prevention, and emerging viral infections."}
  # - {year: 2008-2011, where: "at Working Families Party", what: "Field Manager & Administrative Assistant", description: "Responsible for payroll, managing employees' healthcare coverage, bank deposits, and data entry. Organized informational events for the public, and served as Field Manager for multiple election and fundraising campaigns."}
  
bibliography: mypapers.bib
csl: apa.csl
nocite: '@*'
---

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library("tidyverse")
setwd("/Users/lucydelaney/rmd-cv/")

```

# Honors, Fellowships \& Awards
\vspace{-0.55cm}

\begin{itemize}[noitemsep]
\item[]{2020 \hspace{22mm} Recipient of the Biological Sciences Department Graduate Teaching Award for BIOS 220}
\item[]{2018 \hspace{22mm} Recipient of the Biological Sciences Department Travel Award}
\item[]{2018 \hspace{22mm} Recipient of the Biological Sciences Department Graduate Teaching Award for BIOS 430}
\item[]{2017 \hspace{22mm} Accepted to NSF-funded summer workshop on diversification rates \& macroevolution}
\item[]{2017 \hspace{22mm} Recipient of the Biological Sciences Department Travel Award}
\item[]{2017 \hspace{22mm} Accepted to \href{https://www.arboretum.harvard.edu/tracing-evolution-form-function/}{MicroMORPH Plant Anatomy summer course} at Harvard University}
\end{itemize}

# Extracurricular
\vspace{-0.55cm}

\begin{itemize}[noitemsep]
\item[]{2020-Present \hspace{9.1mm} Developed \href{https://github.com/ledelaney/220bb-calculator}{R functions for automated Blackboard grade finalization}}
\item[]{2020-Present \hspace{9.1mm} Created a website to manage student materials and tutorials in  \href{https://ledelaney.org/BIOS_220/}{BIOS 220: Genetics}}
\item[]{2020 \hspace{22mm} Participant in the \href{https://chircollab.github.io/}{2020 Chicago R Collaborative Conference}}
\item[]{2018 \hspace{22mm} Created programming tutorials for use in \href{https://github.com/ledelaney/GeneralEcologyMaterials}{BIOS 331: General Ecology Laboratory}}
\item[]{2017-Present \hspace{9.1mm} Reviewer for International Journal of Botany, Oxford Bibliographies}
\item[]{2016 \hspace{22mm} General horticulture volunteer at Garfield Park Conservatory}
\end{itemize}

# Presentations
\vspace{-0.55cm}

```{r, eval = T, echo = FALSE, message = FALSE, warning = FALSE}
presentations <- read_csv(file = "presentations.csv", col_names = T, na = c(NA, "", " "), trim_ws = T, skip_empty_rows = T) %>%
  arrange(invited, desc(when))

```

```{r, eval = T, results = "asis", message = FALSE, warning = FALSE, echo = FALSE}
not.invited <- presentations %>%
  filter(invited == 0) %>%
  arrange(-when)
glue::glue_data(not.invited, "**>where<** >what< \\fn{>when<}",
                " \\vspace{-0.35cm} ",
                "\\begin{quote}>gsub('\\\\*', '', who)<, \\href{>link<}{>title<.}\\end{quote}",
                .open = ">", .close = "<")

#{\">title<.\"}
```

\section{Publications}

\vspace{-0.55cm}
