---
output:
  pdf_document:
    latex_engine: xelatex
    template: template.tex
date: April 28, 2020
first: "Lucy E"
last: "Delaney"
email: "ldelan5@uic.edu"
address: "Chicago, IL 60622"
website: "ledelaney.github.io/"
googlescholar: 
orcid: 
programming: "R"
languages: "$\LLaTeX$, HTML, Markdown, & RMarkdown"
github: "ledelaney"
twitter: 
licenses: "Illinois Substitute Teaching License & FCC Technician Class Radio License"
interests: "Evolution outreach & education, macroevolution, the evolution of plant breeding systems, the nature of adaptation, data manipulation & visualization with `tidyverse`, `R` for undergraduate education"
edu:
  - {degree: PhD student, where: University of Illinois at Chicago, description_1: "in Ecology & Evolutionary Biology", description_2: "Thesis: _The Process of Natural Selection: Resultant patterns and how we understand them_"}
  - {degree: MA, where: "CUNY: Hunter College", description_1: "in Molecular & Cellular Biology, 2016"}
  - {degree: BS, where: "CUNY: John Jay College", description_1: "in Forensic Molecular Biology, Philosophy, 2012"}
  
class:
  - {year: "2019-Present", what: "BIOS 220", description_1: "Molecular and Mendelian Genetics", description_2: "Sophomore-level course focusing on Mendelian inheritance patterns and molecular mechanisms of inheritance. Helped managed transition from in-person to online format. Responsible for teaching discussion section, creating digital course materials and exams, grading, and Blackboard administration."}
  - {year: "Spring 2019", what: "BIOS 230", description_1: "Ecology and Evolution", description_2: "Sophomore-level course with emphasis on basic ecological systems, ecosystem dynamics, and evolutionary principles. Responsible for weekly office hours, assignment creation, and grading."}
  - {year: 2017-2018, what: "BIOS 430", description_1: "Evolution", description_2: "Upper-division, programming-focused course on evolutionary theory and principles. Responsible for weekly office hours and debugging, quiz materials, and grading of `R` programming assignments."}
  - {year: 2016-2017, what: "BIOS 120", description_1: "Biology of Populations and Communities", description_2: "Introductory biology laboratory course with emphasis on ecological and evolutionary principles. Responsible for weekly laboratory instruction, office hours, and grading."}

work:
  - {year: "2018-Present", where: "at Nurturing Wisdom Tutoring", what: "Tutor", description: "Highly-rated individual tutoring for grades 7-12 in test preparation (SATs and HSETs), science, mathematics, and writing."}
  - {year: 2012-2015, where: "at NYC Office of Chief Medical Examiner", what: "Forensic Molecular Biologist", description: "Examined evidence for the presence of biological fluids, performed serological and DNA analysis techniques, analyzed data and performed statistical analysis, wrote reports, and provided expert scientific testimony in court."}
  - {year: 2011-2012, where: "at NYC Deptartment of Health", what: "Health Research Intern", description: "Accepted to the Health Research Training Program for a year-long internship with the Bureau of Environmental Disease Prevention. Received training in disease epidemiology, emergency preparedness and response, public health and outreach programs in environmental disease control and prevention, and emerging viral infections."}
  - {year: 2008-2011, where: "at Working Families Party", what: "Field Manager & Administrative Assistant", description: "Responsible for payroll, managing employees' healthcare coverage, bank deposits, and data entry. Organized informational events for the public, and served as Field Manager for multiple election and fundraising campaigns."}
  
bibliography: mypapers.bib
csl: apa.csl
nocite: '@*'
---

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library("tidyverse")
setwd("/Users/lucydelaney/rmd-cv/")

```

# Extracurricular
\vspace{-0.55cm}

+ 2019-Present \hspace{9.1mm} Created a website to manage student materials and tutorials in  \href{https://ledelaney.github.io/bios220/}{BIOS 220: Genetics}
+ 2017-Present \hspace{9.1mm} Reviewer for International Journal of Botany, Oxford Bibliographies
+ 2018 \hspace{22mm} Created programming tutorials for use in \href{https://github.com/ledelaney/GeneralEcologyMaterials}{BIOS 331: General Ecology Laboratory}
+ 2018 \hspace{22mm} Recipient of the Biological Sciences Department Graduate Teaching Award
+ 2017 \hspace{22mm} Accepted to NSF-funded summer workshop on diversification rates & macroevolution
+ 2017 \hspace{22mm} Accepted to \href{https://www.arboretum.harvard.edu/tracing-evolution-form-function/}{MicroMORPH Plant Anatomy summer course} at Harvard University
+ 2016 \hspace{22mm} General horticulture volunteer at Garfield Park Conservatory

# Presentations
\vspace{-0.55cm}

```{r, eval = T, echo = FALSE, message = FALSE, warning = FALSE}
presentations <- read_csv(file = "presentations.csv", col_names = T, na = c(NA, "", " "), trim_ws = T, skip_empty_rows = T) %>%
  arrange(invited, desc(when))

```

```{r, eval = T, results = "asis", message = FALSE, warning = FALSE, echo = FALSE}
not.invited <- presentations %>%
  filter(invited == 0) %>%
  arrange(-when)
glue::glue_data(not.invited, "**>where<** >what< \\fn{>when<}",
                " \\vspace{-0.35cm} ",
                "\\begin{quote}>gsub('\\\\*', '', who)<, \\href{>link<}{>title<.}\\end{quote}",
                .open = ">", .close = "<")

#{\">title<.\"}
```

# Publications
\vspace{-0.55cm}

