
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%PANDOC SPECIFIC SHIT, TAKEN FROM ANOTHER TEMPLATE...

\documentclass[11pt,article,oneside]{memoir}   

%Deal with margins and other geometry stuff
\usepackage[]{geometry}
\usepackage[document]{ragged2e}
\usepackage{fontspec}

\defaultfontfeatures{Path = /usr/local/texlive/2020/texmf-dist/fonts/opentype/public/fontawesome/}

\usepackage{fontawesome}
\setmainfont{MinionPro-Regular.otf}[
Path = /Library/Fonts/minion-pro-cufonfonts/,
BoldFont = MinionPro-Bold.otf,
ItalicFont = MinionPro-It.otf,
BoldItalicFont  = MinionPro-BoldIt.otf]

\def\myauthor{Lucy E Delaney}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myaffiliation{University of Illinois at Chicago}
\def\myaddress{Department of Biological Sciences}
\def\myemail{ldelan5@uic.edu}
\def\myweb{http://ledelaney.github.io}
\def\myphone{(718) 644-8035}
\def\mytwitter{@emergentlylucy}
\def\myversion{}
\def\myrevision{}


\def\myaffiliation{University of Illinois at Chicago}
\def\myauthor{Lucy Delaney}
\date{} % not used (revision control instead)
\def\mykeywords{Lucy, Delaney, Lucy Delaney, Vita, CV, Resume, Biology}


% Need to include this for refs with Pandoc

%Double-spacing or whatever...

%Some of this is math package stuff, but honestly i don't really get
%what most of it is doing
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\usepackage{wasysym}

%Numbered section spacing
\setcounter{secnumdepth}{0}

%For LIST spacing
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% LUCY'S DOCUMENT PREAMBLE AND PACKAGES

\widowpenalty10000
\clubpenalty10000

\usepackage{pdflscape}
\usepackage[dvipsnames]{xcolor}
\definecolor{maroon}{HTML}{ab2e4b}
\definecolor{light-gray}{gray}{0.95}

\usepackage{tcolorbox}
\newtcolorbox{blackbox}{
  colback=light-gray,
  colframe=black,
  coltext=black,
  boxsep=2pt,
  arc=4pt}

%\usepackage[round]{natbib}
\usepackage[natbibapa]{apacite} 
\usepackage[hyphens]{url}


%Bunch of hyperlink shit
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=violet,
    filecolor=magenta,      
    urlcolor=violet,
    citecolor = black
}

%Need all these for graphics and tables
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{array}

\usepackage{float}
%\floatplacement{table}{p}
%\restylefloat{table}
%\newfloat{type}{placement}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% START OF THE DOCUMENT BODY
\begin{document}

%% Choose fonts for use with xelatex
%% Minion and Myriad are widely available, from Adobe. 
%% Pragmata is available to buy at http://www.fsd.it/fonts/pragma.htm
%% and is worth every penny. Any good monospace font will work fine, though.
%% Consolas or inconsolata are good alternatives.
%\setromanfont[Mapping={tex-text}, 
%  Numbers={OldStyle},
%  Ligatures={Common}]{Minion Pro}
%\setsansfont[Mapping=tex-text,
%  Ligatures={Common}, 
%  Colour=AA0000]{Unit-Medium}
%\setmonofont[Mapping=tex-text,Scale=0.72]{PragmataPro} 

%\newfontface\scheader[SmallCapsFont={Minion Pro},SmallCapsFeatures={Letters=SmallCaps}]{Minion Pro}

%\newfontface\addressblock[Mapping={tex-text}, 
%  Numbers={OldStyle},
%  Ligatures={Common}]{Minion Pro Medium Caption}

  %%%------------------------------------------------------------------------
%%% Local commands
%%%------------------------------------------------------------------------

%% Marginal header
%% Note: as the document goes on you may need to introduce a (gradually increasing)
%% \vspace element to keep the marginal header pleasingly aligned with the first 
%% item in the body text. Like this: \marginhead{{\vskip 0.4em}Grants}, or 
%% \marginhead{{\vskip 0.8em}Service}. Experiment as needed.

\newcommand{\marginhead}[1]{\textcolor{red}{\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright #1}}}}}


%% [optional] custom ampersand (font consistent with the one chosen above)
% \newcommand{\amper}{{\fontspec[Scale=.95,Colour=AA0000]{Minion Pro Medium}\selectfont\&\,}}

%% No bullets on labels
\renewcommand{\labelitemi}{~} 

%% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
%\def\ind{\hangindent=18pt\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%%%------------------------------------------------------------------------
%%% Page layout
%%%------------------------------------------------------------------------

% These lines will insert git revision info in the footer, using the vc
% package---see docs for vc package for details. Comment out this line
% if you're not using vc, and also remove the \input{vc} line above.
%\pagestyle{kjh}
%\thispagestyle{kjhgit}



%%%%%%%%%%%%%% DOCUMENT BODY
\noindent

\begin{minipage}{.65\textwidth}
\vspace{1mm}
  {\footnotesize \noindent{\LARGE \textsc{lucy delaney}}\\ \href{http://bios.uic.edu}{Department of Biological Sciences} \\ University of Illinois at Chicago \\ \vspace{-0.05in} Chicago, \textsc{il} 60622}
\end{minipage}
\hfill
\begin{minipage}{.65\textwidth}
{\footnotesize \faPhone \ \myphone} \\
{\scriptsize \faTwitter \  \texttt{\href{http://twitter.com/emergentylucy}{\mytwitter}}}\\
{\scriptsize \faEnvelope \  \texttt{\href{mailto:\myemail}{\myemail}}}\\
{\scriptsize \faGithub \ \texttt{\href{\myweb}{\myweb}}}


\end{minipage}

\bigskip       
\reversemarginpar

\bigskip

\marginhead{\sffamily \textbf{\textcolor{maroon}{education}}}

\ind PhD candidate in Evolutionary Biology, 2016--Present.

\ind Visiting Associate Professor of Sociology, Duke University,
2008--2009.

\ind Associate Professor of Sociology, University of Arizona, 2008.

\ind Research Fellow, Social and Political Theory Program, Research
School of Social Sciences, Australian National University, 2003--2006.

\ind Assistant Professor of Sociology, University of Arizona,
2001--2008.

\bigskip

\marginhead{\sffamily {{\vskip -0.23em} education}}

\ind Ph.D, Sociology, Princeton University, 2001.

\ind \hspace{0.35in} \footnotesize Dissertation:
\emph{Exchange in Blood and Organs}.\newline Winner, American
Sociological Association's Dissertation
Award.\normalsize \vspace{0.05in}

\ind M.A., Sociology, Princeton University, 1998.

\ind M.A., Sociology, First Class, National University of Ireland
(Cork), 1994.

\ind \hspace{0.35in} \footnotesize Thesis:
\emph{The Language of Influence: Public Debate and the Politics of the X-case.}
\normalsize \vspace{0.01in}

\ind B.A. (Joint Hons.), First Class, National University of Ireland
(Cork), 1993.

\bigskip

\marginhead{\sffamily {\vskip 0.35em} publications}
\medskip

\noindent\emph{Book \vspace{0.01in}}

\ind  Kieran Healy. 2006.
\emph{\href{http://www.lastbestgifts.com}{Last Best Gifts: Altruism and the Market for Human Blood and Organs}}.
Chicago:\textasciitilde University of Chicago Press. \vspace{0.05in}

\ind \hspace{0.35in} \footnotesize Winner, Association for Research on
Nonprofit Organizations and Voluntary Action (ARNOVA) Outstanding Book
Prize. Finalist, C. Wright Mills Award.

\vspace{-0.075in}

\normalsize

\bigskip

\noindent\emph{Journal articles \vspace{0.05in}}

\ind Forthcoming. Kieran Healy and James Moody. ``Data Visualization in
Sociology.'\,' \emph{Annual Review of Sociology.}

\ind Marion Fourcade and Kieran Healy. 2013.
``\href{http://kieranhealy.org/files/papers/classification-situations.pdf}{Classification Situations: Life-chances in the Neoliberal Era}.'\,'
\emph{Accounting, Organizations, and Society}
38:\textasciitilde559--572.

\ind Kieran Healy and Kimberly R. Krawiec. 2012.
``\href{http://kieranhealy.org/files/papers/custom-contract-kidney.pdf}{Custom, Contract, and Kidney Exchange}.'\,'
\emph{Duke Law Journal} 62:\textasciitilde645--670.

\ind Kieran Healy. 2011. ``Counting and Commodifying.'\,'
\emph{Washington University Journal of Law and Policy}.
35:\textasciitilde337--347.

\noindent\emph{Essays and reviews \vspace{0.05in}}

\ind Kieran Healy. 2011.
``\href{http://www.kieranhealy.org/files/reviews/karpik-review.pdf}{Judgment and Distinction}.'\,'
\emph{Socio--Economic Review} 9:\textasciitilde787--800.

\ind Kieran Healy. 2011.
``\href{http://polmeth.wustl.edu/methodologist/tpm_v18_n2.pdf}{Choosing your Workflow Applications}.'\,'
\emph{The Political Methodologist} 18 (2):\textasciitilde9--18.

\bigskip

\marginhead{\sffamily {\vskip 0.5em}selected \newline conference \newline presentations \newline since 2007}
\medskip

\ind ``Dealing with Awkward Relations.'\,' Conference on New Theoretical
Directions in Economic Sociology, Stockholm, September 2013.

\ind ``Credit Scores and the Moralization of Inequality.'\,' Annual
Meetings of the American Sociological Association, New York, August
2013.

\bigskip

\marginhead{\sffamily {\vskip 0.6em}grants,\newline honors, \newline \& awards}
\medskip

\ind Residential Fellowship, Center for Advanced Study in the Behavioral
Sciences, Stanford University, 2008-09.

\ind Association for Research on Nonprofit Organizations and Voluntary
Action (ARNOVA) Outstanding Book Prize, 2007.

\ind Finalist, Society for the Study of Social Problems (SSSP), C.
Wright Mills Award, 2007.

\ind Rogers Program in Law and Society, Faculty Research Award,
University of Arizona, 2006.

\ind Participant, Summer Institute on
\emph{Economy and Society: Trajectories of Capitalism}, Center for
Advanced Study in the Behavioral Sciences, 2006.

\ind University of Arizona SBSRI/Center for Applied Spatial Analysis.
Geographical Information Systems Research Assistance Program Award.
``The Geography of Organ Procurement'\,', 2003.

\marginhead{\sffamily {\vskip 1.12em}service to the \newline profession}
\medskip

\medskip

\marginhead{{\vskip 0.9em}Service to the \newline Profession}
\medskip

\medskip

\end{document}
